Transfer Learning in Visual and Relational Reasoning

### 2019-11-22 Transfer_Learning/arxiv_version/arxiv_paper_main.tex
Title + author Figure placement

%%%%%%%%% TITLE
\title{Transfer Learning in Visual and Relational Reasoning\footnote{%
		This work was primarily done at IBM Research AI.}}

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
	T.S. Jayram\thanks{IBM Research AI. \textit{Almaden Research Center, San Jose, CA, USA}.} \and  
	Vincent Marois\thanks{IBM Research AI. \textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \and 
	Tomasz Kornuta\thanks{Nvidia Research. \textit{Santa Clara, CA, USA}.} \and 
	Vincent Albouy\thanks{} \and 
	Emre Sevgen\thanks{Citrine Informatics}  \and 
	Ahmet Ozcan\footnotemark[2]
}

>>>>

%%%%%%%%% TITLE
\title{Transfer Learning in Visual and Relational Reasoning}

%%%%%%%%% AUTHORS
% WILL NEED TO REARRANGE THE AUTHORS LIST & GET CORRECT INSTITUTIONS / EMAILS
\author{%
T.S. Jayram\thanks{\textit{Almaden Research Center, San Jose, CA, USA}.} \hspace{1cm} \and  
Vincent Marois\thanks{\textit{Thomas J. Watson Research Center, Yorktown Heights, NY, USA}.} \hspace{1cm} \and 
Tomasz Kornuta\thanks{Currently at Nvidia. \textit{Santa Clara, CA, USA}.} \and
\hspace{2cm} Vincent Albouy\footnotemark[1]  \hspace{1cm} \and 
Emre Sevgen\thanks{Currently at Citrine Informatics}  \hspace{1cm} \and 
Ahmet S. Ozcan\footnotemark[1] \and \\
IBM Research AI
}
